### 2019-10-19 Manuscript/manuscript.tex
touch of text about paleogeo models

There are more published models that show snapshots at given time intervals \cite[e.g.]{Li2008a}.  The synthesis of \citet{Pesonen2012a} developed reconstructions at various Proterozoic time slices.

>>>>

There are more published models that show snapshots and publish rotation parameters associated with given time intervals (e.g. the rotation model of \citealp{Li2008a}). The position for Laurentia implied by the snapshot of the \cite{Li2008a} model is shown in Figure \ref{fig:Laurentia_paleolatitude}.

 The synthesis of \citet{Pesonen2012a} developed reconstructions at various Proterozoic time slices.
